\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{ulem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\usepackage{CormorantGaramond}
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Style block for sections with text
\titleformat{\section}
{\vspace{-4pt}\scshape\raggedright\large}
{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

% Style block for sections without text
\titleformat{name=\section, numberless}
{\vspace{-4pt}\scshape\raggedright\large}
{}{0em}{}

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemList}[1]{
  \item\textbf{\small
    {#1 \vspace{-2pt}}
  }
}\vspace{-7pt}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\experianceSubheading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\freelanceListStart}{\begin{itemize}[label={}]}
\newcommand{\freelanceListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\freelanceItemsListStart}{\begin{itemize}[label={$\vcenter{\hbox{\tiny$\bullet$}}$}]}
\newcommand{\freelanceItemsListEnd}{\end{itemize}\vspace{0pt}}

\begin{document}

\begin{center}
    \textbf{\Huge \scshape Tarn Barford} \\ \vspace{1pt}
    \small +49 152 234 79181 $|$
    \href{mailto:tarn@tarnbarford.net}{\uline{tarn@tarnbarford.net}} $|$
    \href{https://tarnbarford.net}{\uline{tarnbarford.net}} $|$
    \href{https://github.com/tarnacious}{\uline{github.com/tarnacious}}
\end{center}

\section*{}
  \small { Skilled software engineer with extensive experience in developing, maintaining, deploying, and operating software systems. Demonstrated excellence in diverse roles, ranging from engineering and consulting to technical leadership and senior management. }


\section{Experience}
  \resumeSubHeadingListStart
    \experianceSubheading
      {Chief Technology Officer, brainsome GmbH}{Jan 2023 – June 2023}
      \resumeItemListStart
        \resumeItem{Developed a strategy to deliver features while gradually replacing legacy systems, resulting in a reduction of over 100,000 lines of code or 25\% during the first half of 2023. }
        \resumeItem{Managed the continue development of efficient improvements, resulting in a 25\% reduction in hosting costs during the first half of 2023.}
        \resumeItem{Formulated and communicated a compelling technical vision, motivating and guiding the efforts of the development team.}
        \resumeItem{Devised a strategic plan to facilitate the orderly winding down of the business following the withdrawal of a significant investor.}
      \resumeItemListEnd
    \experianceSubheading
      {Lead Developer, brainsome GmbH}{Jun 2018 – Dec 2022}
      \resumeItemListStart
        \resumeItem{Managed teams of internal and external developers, ensuring efficient collaboration and delivery of projects.}
        \resumeItem{Spearheaded the transition of responsibilities from external teams to an internal team, overseeing the technical aspects of the process.}
        \resumeItem{Overcame major business and technical challenges posed by an off-shore team reluctant to relinquish development and operational responsibilities.}
        \resumeItem{Responsible for end-to-end software development, infrastructure management, and site reliability of multiple web properties.}
        \resumeItem{Technologies used Java, Javascript, Go, Ruby, Postgresql,
        Redis, Elasticsearch, RabbitMQ, Elasticsearch, MongoDB, Puppet,
        Kubernetes, Icinga2, Bareos and Kibana.}
      \resumeItemListEnd
    \experianceSubheading
      {Freelance}{July 2015 - June 2018}
      \freelanceListStart
        \resumeItemList{Advertile Mobile GmbH}
          \freelanceItemsListStart
            \resumeItem{Played a key role in devising creative and innovative solutions for tracking incentivized app installations on both Android and iOS platforms.}
            \resumeItem{Led the ongoing development of the AngularJS website which was as the key interface for the product.}
            \resumeItem{Contributed to the ideation of features and incentives aimed at enhancing key metrics, including the 7-day user retention rate. Conducted A/B tests to evaluate their effectiveness and decisively implemented or discarded them based on the outcomes.}
          \freelanceItemsListEnd
        \resumeItemList{2txt – natural language generation GmbH}
          \freelanceItemsListStart
            \resumeItem{Proficiently performed data collection, cleaning, and formatting for NLP training purposes.}
            \resumeItem{Developed a web platform showcasing and facilitating the sale of NLP services.}
          \freelanceItemsListEnd
        \resumeItemList{brainsome GmbH}
          \freelanceItemsListStart
            \resumeItem{Served as an consultant specializing in search development, providing expert guidance and solutions.}
            \resumeItem{Made substantial contributions to the Ruby on Rails project, significantly enhancing the development process and enabling the rapid delivery of features.}
          \freelanceItemsListEnd
      \freelanceListEnd
    \experianceSubheading
      {Retresco GmbH, Software Engineer}{July 2012 - June 2015}
      \resumeItemListStart
        \resumeItem{Collaborated as a key member of a development team responsible for creating a system that delivered recommended articles for major German newspapers.}
        \resumeItem{Provided expert consultation to diverse clients, specializing in integrating search and natural language capabilities into their products.}
        \resumeItem{Actively engaged with the developer community, organizing and hosting meetups and workshops at Retresco offices to foster knowledge sharing and networking.}
      \resumeItemListEnd
    \experianceSubheading
      {Freelance}{January 2012 - May 2012}
      \freelanceListStart
        \resumeItemList{Get The World Moving}
          \freelanceItemsListStart
            \resumeItem{Developed a product called Trailblazer for Get The World Moving}
            \resumeItem{The product is successfully delivered on time and budget}
            \resumeItem{It is built with Ruby on Rails, Redis, MySQL and Backbone and Google Maps}
          \freelanceItemsListEnd
      \freelanceListEnd
    \experianceSubheading
      {Helsinki Agency, Software Engineer}{December 2009 - January 2012}
      \resumeItemListStart
        \resumeItem{Worked with creatives on successful pitches and
        implementations of inovative digital campaigns}
        \resumeItem{Significant contributer on an event called Get The World
        Moving that is developed internally}
        \resumeItem{Get The World Moving is later split into its own company,
        acquired by Virgin Group and rebranded as Virgin Pulse.}
      \resumeItemListEnd
    \experianceSubheading
      {Hardcat, Software Engineer}{January 2009 - October 2009}
      \resumeItemListStart
        \resumeItem{Co-contributer in the development of a .NET web interface to an Asset Management product written in C++}
        \resumeItem{Collaborated with the C++ product team on the .NET integration and fixing bugs in the C++ API}
        \resumeItem{Proposed various strategies to improve the .NET web interface feature set that were adapted}
      \resumeItemListEnd
    \experianceSubheading
      {think!, Software Engineer}{January 2006 - January 2009}
      \resumeItemListStart
        \resumeItem{Key contributer in a successful migration of a Classic ASP business-to-business price comparison e-commerce application to the .NET framework}
        \resumeItem{Selected with a prooduct manager for four-week on-site collaboration in Ireland with OpenJaw Technologies to integrate flight booking capabilities. }
        \resumeItem{Lead developer of the integration OpenJaw platform to enbable flight booking capabilities on the platform.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Royal Melbourne Institute of Technology}{Melbourne, Australia}
      {Bachelor of Engineering (Electronic), Honors Class 2a}{Mar. 2000 -- May 2004}
  \resumeSubHeadingListEnd

\section{Languages}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{English}{: Native} \\
     \textbf{German}{: B1}
    }}
 \end{itemize}

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Typescript, Javascript, Ruby, Java, Clojure, SQL } \\
     \textbf{Tools}{: neovim, tmux, git, bash, strace, curl, kubectl, awscli, jq, xmllib2, GnuPG, ssh, systemctl, openssl } \\
     \textbf{Orchestration}{: Kubernetes, Helm, Puppet, Ansible } \\
     \textbf{Cloud}{: AWS, GCP, Digitial Ocean, Hetzner } \\
     \textbf{Monitoring}{: Icinga2, Logstash, Kibana, Munin, Prometheus, Grafana } \\
     \textbf{CI}{: Jenkins, Gitlab CI } \\
     \textbf{Virtualization}{: KVM, qemu, docker } \\
     \textbf{Datbases}{: Postgres, Elasticsearch, Redis, MongoDB, RabbitMQ } \\
     \textbf{System Tools}{ : systemd, UFW, iptables, nginx, haproxy, sshd }
     \textbf{Linux Distributions}{: Debian, Ubuntu, NixOS, Arch Linix, Busybox } \\
    }}
 \end{itemize}

\end{document}
